Dissertation Manuscript

### 2024-06-21 Manuscript/manuscript.qmd
re-render all formats and tweak afiliations

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

@@

  Test2 -> Test3
}
```
:::

>>>>

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]

@@

  Test2 -> Test3
}
```
:::
```{r}

### 2024-06-21 Sections/HTW.qmd
re-render all formats and tweak afiliations

---
title: HTW Project
date: last-modified
author:
- name: Thomas E. Gorman
  affiliations: 
  - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
---

_______________________________________________________________________________

@@

 [{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \
_______________________________________________________________________________

>>>>

---
title: HTW Project
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
page-layout: full
code-fold: true
code-tools: true
cache: true
toc: true
toc-location: body
toc-title: Contents
format-links: [hikmah-manuscript-pdf, gfm]
format: 
  html: 
    date: last-modified
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: htw_hugo.md
  gfm:
    echo: false
    output-file: htw_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "htw_dis.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
execute: 
  warning: false
  eval: true
---

::: {.content-visible when-format="html"}
_______________________________________________________________________________

@@

 [{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \
_______________________________________________________________________________
:::

### 2024-06-21 Sections/IGAS.qmd
re-render all formats and tweak afiliations

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
author:
- name: Thomas E. Gorman
  affiliations: 
  - Department of Psychological and Brain Sciences, Indiana University-Bloomington
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
format:
  html: default
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: igas_hugo.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "igas_dis.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
prefer-html: true
---

>>>>

---
title: IGAS Project
subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
format-links: [hikmah-manuscript-pdf, gfm]
format:
  html: default
  hugo-md:
    echo: false
    include: false
    html-math-method: mathjax
    output-file: igas_hugo.md
  gfm:
    echo: false
    output-file: igas_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "igas_dis.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  # hikmah-manuscript-docx: 
  #   prefer-html: true
  #   echo: false
execute: 
  warning: false
  eval: true
editor: 
  markdown: 
    wrap: 72
prefer-html: true
---

### 2024-06-21 Sections/full.qmd
re-render all formats and tweak afiliations

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas Gorman
  affiliation: Indiana University
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  orcid: 0000-0001-5366-5442
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

### 2024-06-21 paper.qmd
tweaks with icons, added iconify
re-render all formats and tweak afiliations

---
title: Dissertation Manuscript
toc: false
page-layout: full
---

>>>>

---
title: Dissertation Manuscript
subtitle: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
toc: false
page-layout: full
---

{{< iconify <icon> >}}
